The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-04-25 paper/ms.tex
Remove neighborhood column from table

\begin{deluxetable*}{cCCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities
from \citet{2018AA...616A..10G}. Actions are computed using the method outlined in Section~\ref{ssec:action_comp}, with typical values for the Galactocentric coordinate system parameters. These are only shown to illustrate the general types of orbits open clusters are on. The neighborhood column is explained in more
detail in Section~\ref{sssec:reconstruction}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{$N_{\text{memb}}$} & \colhead{distance} & \colhead{$J_R$} &
\colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} & \colhead{neighborhood} \\ 
\colhead{ } & \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$} & \colhead{$\mathrm{pc}$}}
\startdata
alphaPer & 740 & 174.9 & 20 & -1700 & 0.005 & 11 & 352\tablenotemark{b} & 57 \\
Blanco1 & 489 & 237.2 & 2 & -1800 & 2 & 210 & 410\tablenotemark{c} & 1460 \\
ComaBer & 153 & 85.9 & 2 & -1900 & 0.7 & 140 & 112\tablenotemark{d} & 522\\
Hyades & 515 & 47.5 & 20 & -1800 & 0.3 & 80 & 400\tablenotemark{e} & 462 \\
IC2391 & 325 & 151.6 & 6 & -1800 & 0.02 & 20 & \nodata & \nodata \\
IC2602 & 492 & 152.2 & 10 & -1700 & 0.3 & 89 & \nodata & \nodata \\
NGC2451A\tablenotemark{a} & 400 & 193.7 & 6 & -1800 & 0.2 & 73 & \nodata & \nodata \\
Pleiades & 1326 & 135.8 & 20 & -1700 & 0.4 & 96 & 800\tablenotemark{f} & 685 \\
Praesepe & 938 & 186.2 & 20 & -1800 & 0.6 & 120 & 550\tablenotemark{d} & 781
\enddata

>>>>

\begin{deluxetable*}{cCCCCCCCC}
\tablecaption{Relevant dynamical parameters for the $9$ open clusters within
$250\,\pc$ of the Sun, using the relevant initial positions and velocities
from \citet{2018AA...616A..10G}. Actions are computed using the method outlined in Section~\ref{ssec:action_comp}, with typical values for the Galactocentric coordinate system parameters. These are only shown to illustrate the general types of orbits open clusters are on. The neighborhood column is explained in more
detail in Section~\ref{sssec:reconstruction}.\label{tab:real_clusters}}
\tablehead{\colhead{cluster} & \colhead{$N_{\text{memb}}$} & \colhead{distance} & \colhead{$J_R$} &
\colhead{$J_{\phi}$} & \colhead{$J_z$} & \colhead{$z_{\text{max}}$} & \colhead{mass} \\ 
\colhead{ } & \colhead{ } &
\colhead{$\mathrm{pc}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{kpc\,km\,s^{-1}}$} & \colhead{$\mathrm{kpc\,km\,s^{-1}}$} &
\colhead{$\mathrm{pc}$} & \colhead{$M_{\odot}$}}
\startdata
alphaPer & 740 & 170 & 20 & -1700 & 0.005 & 11 & 352\tablenotemark{b} \\
Blanco1 & 489 & 240 & 2 & -1800 & 2 & 210 & 410\tablenotemark{c} \\
ComaBer & 153 & 90 & 2 & -1900 & 0.7 & 140 & 112\tablenotemark{d} \\
Hyades & 515 & 50 & 20 & -1800 & 0.3 & 80 & 400\tablenotemark{e} \\
IC2391 & 325 & 150 & 6 & -1800 & 0.02 & 20 & \nodata \\
IC2602 & 492 & 150 & 10 & -1700 & 0.3 & 89 & \nodata \\
NGC2451A\tablenotemark{a} & 400 & 190 & 6 & -1800 & 0.2 & 73 & \nodata \\
Pleiades & 1326 & 140 & 20 & -1700 & 0.4 & 96 & 800\tablenotemark{f} \\
Praesepe & 938 & 190 & 20 & -1800 & 0.6 & 120 & 550\tablenotemark{d}
\enddata
